Predicting sales of newly published books

### 2015-10-13 paper.tex
add new contents explaining the feature selection methods used
fixing some broken refs

  \item  First, after the editorial company has provided the raw data, taken 
  directly from its database, a feature selection is carried out, as it is 
  an effective dimensionality reduction technique and an essential preprocessing 
  method to remove noise features \cite{Balaji2004}. The idea of these 
  algorithms is searching the space of attribute subsets to find out which one 
  in the data works best for classification or prediction.
  In this stage, the information obtained using several feature selection 
  methods as well as analyzing the SOM cluster method results is used to 
  remove some unrelated variables and selects the best variables to be 
  considered in the forecasted model. % we will use pre-sales data.
  This task may help to identify leading indicators to be used by the 
  forecasting methods in order to improve the accuracy of future forecasts.

@@

@@

  %  El proceso que seguimos, resumido para el paper, es:
  %  
  %  [43 entradas] en 2013-01 vamos a tomar 
  %  	pb_noneg.csv para obtener pb_ventas.csv (es el pb_ventas.arff)
  %  
  %  [13 entradas] en 2013-02-08 vamos a tomar 
  %  	controlado_reducido.csv.arff (197 líneas)
  %  	pbenero.csv.arff (5656 líneas)
  %  
  %  [7 entradas; materia editorial] en 2013-02-25 vamos a tomar
  %  	pbRAWtrn.arff
  %  	pbRAWtst.arff

>>>>

  \item  First, after the editorial company has provided the raw data, taken 
  directly from its database, a feature selection is carried out, as it is 
  an effective dimensionality reduction technique and an essential preprocessing 
  method to remove noise features \cite{Krishnapuram2004}. The idea of these 
  algorithms is searching the space of attribute subsets to find out which one 
  in the data works best for classification or prediction.
  In this stage, the information obtained using several feature selection 
  methods as well as analyzing the SOM cluster method results is used to 
  remove some unrelated variables and selects the best variables to be 
  considered in the forecasted model. % we will use pre-sales data.
  This task may help to identify leading indicators to be used by the 
  forecasting methods in order to improve the accuracy of future forecasts.

@@

%
% TODO: explicar los resultados obtenidos en la selección de variables (1) con el SOM (2) con los métodos de selecc. vars.
%

@@
